noam_data_exploration_v1

### 2024-08-22 noam_data_exploration_v3.Rmd
added shannon diversity for adiv models/effects plots. Adjusted figs to log scale y axis for parity with model.

@@

summary(richness_mod_2) # looks like strong autocorrelation, which makes sense to me
Anova(richness_mod_2)
plot(allEffects(richness_mod_2))
mod_emm <- emmeans(richness_mod_2, ~ habitat * island_side * year_factor) # if we want to compare habitats year to year
richness_plot_info <- plot(mod_emm, plotit = FALSE)
richness_plot_info$year_numeric <- as.numeric(levels(richness_plot_info$year_factor))
(emmeans_graph <- 
  ggplot(data =richness_plot_info) +
  geom_point(aes(y = exp(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = exp(asymp.LCL), ymax = exp(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 5.2, yend = 5.2, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Estimated marginal mean richness\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

@@

(total_turnover_emmeans_graph <- 
  ggplot(data =total_turnover_plot_info) +
  geom_point(aes(y = inv_logit(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Estimated marginal mean total turnover\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

(appearance_turnover_emmeans_graph <- 
  ggplot(data =appearance_turnover_plot_info) +
  geom_point(aes(y = inv_logit(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 0.5, yend = 0.5, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Estimated marginal mean appearance turnover\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

(disappearance_turnover_emmeans_graph <- 
  ggplot(data =disappearance_turnover_plot_info) +
  geom_point(aes(y = inv_logit(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 0.5, yend = 0.5, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Estimated marginal mean disappearance turnover\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

(richness_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_quadrat,
             aes(x = richness_mean, y = cover_cv, colour = island_side, shape = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = richness_cv_emm, aes(x = richness_mean, y = exp(yvar), colour = island_side), size = 2) +
  geom_ribbon(data = richness_cv_emm, aes(x = richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = island_side), alpha = 0.3) +
#   scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~habitat) +

@@

```{r portfolio effects and synchrony transect level,  fig.height = 8, fig.width = 10}
synchrony_cv_mod <- glmmTMB(cover_cv ~ loreau_synchrony*habitat*island_side + (1|site/transect), 
                             family = Gamma(link = "log"),
                          data = diversity_stability_quadrat, na.action = na.pass)
# model.sel(dredge(synchrony_cv_mod)) # top model by far is as specified
r.squaredGLMM(synchrony_cv_mod) # 0.73, 0.74
summary(synchrony_cv_mod)
emmeans(synchrony_cv_mod, pairwise ~ island_side | habitat, var = "loreau_synchrony", at = list(loreau_synchrony = seq(0,1,0.05)))
synchrony_cv_emm <- emmip(synchrony_cv_mod,
                        habitat ~ loreau_synchrony | island_side,
                        at = list(loreau_synchrony = seq(0,1,0.05)), plotit = F, CIs = T)

(loreau_stability_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = loreau_synchrony, y = cover_cv, colour = island_side, shape = habitat), size = 2, alpha = 0.5) + 
 # geom_line(data = synchrony_cv_emm, aes(x = loreau_synchrony, y = exp(yvar), colour = island_side), size = 1) +
 # geom_ribbon(data = synchrony_cv_emm, aes(x = loreau_synchrony, ymin = LCL, ymax = UCL, fill = island_side),
 #             alpha = 0.3) +
   scale_shape_manual(values = habitat_shapes) +
#  facet_wrap(~habitat) +

>>>>

```{r gls shannon, fig.height=10, fig.width=14}
alpha_diversity_quad$logShann <- log(alpha_diversity_quad$shannon + 1)
columns <- c("location", "Intercept", "Slope", "Phi") # names of columns for dataframe
gls_shann_coefficients <- # new dataframe name
  data.frame(matrix(nrow = length(unique(alpha_diversity_quad$location)), # 1200 quadrats = 1200 different time series
                    ncol = length(columns)) # specified to make sure number of columns doesn't exceed what was specified
             )
colnames(gls_shann_coefficients) <- columns # change column names to what was specified
gls_shann_coefficients$location <- levels(alpha_diversity_quad$location) # populate location column with each quad/time series

  # fit gls for current time series
  loop_mod <- gls(shannon ~ year, correlation =corAR1(form=~year), control = list(singular.ok = TRUE), data = newData)

  # populate appropriate row and column with the relevant coeffcients from gls
  gls_shann_coefficients[i, 2] <- unname(coef(loop_mod)[1])
  gls_shann_coefficients[i, 3] <- unname(coef(loop_mod)[2])
  gls_shann_coefficients[i, 4] <- loop_mod[["modelStruct"]][["corStruct"]]

hist(gls_shann_coefficients$Slope) # looks basically normal, bounded -Inf, Inf

hist(gls_shann_coefficients$Intercept) # same with intercept - although it probably shouldn't be
hist(gls_shann_coefficients$Phi)

gls_shann_coefficients_merged <- merge(gls_shann_coefficients, extra_meta, by = "location")

slope_shann_mod <- glmmTMB(Slope ~ habitat*island_side + (1|island_side/site/transect), data = gls_shann_coefficients_merged)
summary(slope_shann_mod) # pretty low variance in random effects
plot(gls_res <- simulateResiduals(slope_shann_mod))

hist(residuals(slope_shann_mod))
plot(predict(slope_shann_mod) ~ residuals(slope_shann_mod))
Anova(slope_shann_mod)

r.squaredGLMM(slope_shann_mod) # 0.19, 0.22
plot(allEffects(slope_shann_mod))

slope_emm <- emmeans(slope_shann_mod, ~ habitat*island_side) # create emmeans object
slope_plot_info <- plot(slope_emm, plotit = FALSE)
(emmeans_slope_graph <- 
  ggplot(data =slope_plot_info) +
  geom_point(aes(y = the.emmean, x = habitat, colour = island_side), size = 8, position = position_dodge(0.3)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL, x = habitat, colour = island_side), width = 0.2, size = 1.5,
                position = position_dodge(0.3) )+
  geom_hline(yintercept = 0) +
  theme_classic() +
  labs(y = "Estimated maringal mean slope\n", x = "Habitat") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

# Note: not sure I want to include this
emmeans(slope_shann_mod, pairwise ~ island_side | habitat)
# north and east coast not different from each other in backreef
# east and west not different from each other in fringing
# north and west not different from each other outer 10
# no sites different from each other outer 17
slope_est <- as.data.frame(slope_emm) # create df of emmeans estimates

@@

summary(richness_mod_2) # looks like strong autocorrelation, which makes sense to me
Anova(richness_mod_2)
plot(allEffects(richness_mod_2))
mod_emm <- emmeans(richness_mod_2, ~ habitat * island_side * year_factor) # if we want to compare habitats year to year
richness_plot_info <- plot(mod_emm, plotit = FALSE)
richness_plot_info$year_numeric <- as.numeric(levels(richness_plot_info$year_factor))
(emmeans_graph <- 
  ggplot(data =richness_plot_info) +
  geom_point(aes(y = exp(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = exp(asymp.LCL), ymax = exp(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 5.2, yend = 5.2, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  scale_y_log10() +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Estimated marginal mean richness\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

```{r glmm shannon, fig.height = 15, fig.width=25}
shannon_mod <- glmmTMB(
  log(shannon+1) ~ year_factor*habitat*island_side + (1 | site/transect/location) + ar1(year_factor + 0 | location),

  data = alpha_diversity_quad,
  control = glmmTMBControl(optCtrl = list(iter.max = 2000, eval.max = 2000)), na.action = na.pass
) # overspecified but going with it for now

summary(shannon_mod) # looks like strong autocorrelation, which makes sense to me
Anova(shannon_mod)
plot(allEffects(shannon_mod_2))
mod_emm <- emmeans(shannon_mod, ~ habitat * island_side * year_factor) # if we want to compare habitats year to year
shannon_plot_info <- plot(mod_emm, plotit = FALSE)
shannon_plot_info$year_numeric <- as.numeric(levels(shannon_plot_info$year_factor))
(emmeans_graph <- 
  ggplot(data =shannon_plot_info) +
  geom_point(aes(y = exp(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = exp(lower.CL), ymax = exp(upper.CL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 2.5, yend = 2.5, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  scale_y_log10() +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Shannon-Weiner Index (H')\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

(total_turnover_emmeans_graph <- 
  ggplot(data =total_turnover_plot_info) +
  geom_point(aes(y = inv_logit(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 1, yend = 1, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Total turnover\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

(appearance_turnover_emmeans_graph <- 
  ggplot(data =appearance_turnover_plot_info) +
  geom_point(aes(y = inv_logit(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 0.5, yend = 0.5, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Appearances\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

(disappearance_turnover_emmeans_graph <- 
  ggplot(data =disappearance_turnover_plot_info) +
  geom_point(aes(y = inv_logit(the.emmean), x = year_numeric, colour = island_side), size = 8) +
  geom_errorbar(aes(ymin = inv_logit(asymp.LCL), ymax = inv_logit(asymp.UCL), x = year_numeric, colour = island_side), 
                width = 0.2, size = 1.5) +
  geom_segment(aes(y = 0.5, yend = 0.5, x = 2006, xend = 2010), linewidth = 4, alpha = 0.2, colour = "grey") +
  geom_vline(xintercept = 2010, linetype = 2, colour = "black", size = 2) +
  geom_vline(xintercept = 2019, linetype = 2, colour = "red", size = 2) +
  facet_wrap(~habitat) +
  theme_classic() +
  labs(x = "Year", y = "Disappearances\n") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
#        panel.background = element_blank(),
        legend.text = element_text(size=20),
        legend.title = element_text(size=20),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain"),
        strip.text.y = element_text(color = "grey20", size = 25, hjust = .5, vjust = 0, face = "plain") ) )

@@

(richness_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_quadrat,
             aes(x = richness_mean, y = cover_cv, colour = island_side, shape = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = richness_cv_emm, aes(x = richness_mean, y = exp(yvar), colour = island_side), size = 2) +
  geom_ribbon(data = richness_cv_emm, aes(x = richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = island_side), alpha = 0.3) +
#   scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~habitat) +
  scale_y_log10() +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r portfolio effects and synchrony transect level,  fig.height = 8, fig.width = 10}
synchrony_cv_mod <- glmmTMB(cover_cv ~ loreau_synchrony*habitat*island_side + (1|island_side/site/transect), 
                             family = Gamma(link = "log"),
                          data = diversity_stability_quadrat, na.action = na.pass)
# model.sel(dredge(synchrony_cv_mod)) # top model by far is as specified
r.squaredGLMM(synchrony_cv_mod) # 0.78, 0.79
summary(synchrony_cv_mod)
synchrony_cv_effects <- emmeans(synchrony_cv_mod, pairwise ~ island_side | habitat, var = "loreau_synchrony")
synchrony_cv_emm <- emmip(synchrony_cv_mod,
                        habitat ~ loreau_synchrony | island_side,
                        at = list(loreau_synchrony = seq(0,1,0.05)), plotit = F, CIs = T)

(loreau_stability_plot_quad = 
  ggplot(data = diversity_stability_quadrat) +
  geom_point(aes(x = loreau_synchrony, y = cover_cv, colour = island_side, shape = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = synchrony_cv_emm, aes(x = loreau_synchrony, y = exp(yvar), colour = island_side), size = 1) +
  geom_ribbon(data = synchrony_cv_emm, aes(x = loreau_synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = island_side),
             alpha = 0.3) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~habitat) +
   scale_y_log10() +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
